---
title: "Exercise 9"
author: "Lili Benitez"
date: "2024-03-27"
output: html_document
---
```{r}
library(tidyverse)
library(ggplot2)
f<-"https://raw.githubusercontent.com/difiore/ada-2024-datasets/main/Street_et_al_2017.csv"
d<-read_csv(f)
summary(d)
library(skimr)
skim(d)

```
# Plots
  From this dataset, plot brain size (ECV) as a function of social group size (Group_size), longevity (Longevity), juvenile period length (Weaning), and reproductive lifespan (Repro_lifespan).
```{r}
ggplot(aes(x=ECV, y=Group_size), data=d)+
  geom_point()+
  geom_smooth(method="lm")

ggplot(aes(x=ECV, y=Longevity), data=d)+
  geom_point()+
  geom_smooth(method="lm")
ggplot(aes(x=ECV, y=Weaning), data=d)+
  geom_point()+
  geom_smooth(method="lm")
ggplot(aes(x=ECV, y=Repro_lifespan), data=d)+
  geom_point()+
  geom_smooth(method="lm")

```

```{r}
d<-d%>%
  drop_na(ECV)%>%
  drop_na(Group_size)
(b1<-cov(d$ECV, d$Group_size)/var(d$Group_size))
(b0<-mean(d$ECV)-b1*mean(d$Group_size))

m<-lm(ECV~Group_size, data=d)
summary(m) #look the same
```
Repeat the analysis above for three different major radiations of primates - “catarrhines”, “platyrrhines”, and “strepsirhines”) separately. These are stored in the variable Taxonomic_group. Do your regression coefficients differ among groups? How might you determine this?

```{r}
c<-d%>%
  filter(Taxonomic_group=="Catarrhini")
p<-d%>%
  filter(Taxonomic_group=="Platyrrhini")
s<-d%>%
  filter(Taxonomic_group=="Strepsirhini")

(mc<-lm(ECV~Group_size, data=c))
(mp<-lm(ECV~Group_size, data=p))
(ms<-lm(ECV~Group_size, data=s))

(summary(mc))
(summary(ms))
(summary(mp))

mod<-lm(ECV~Group_size*Taxonomic_group, data=d)
summary(mod)
```
The coefficients were different between taxonomic groups, and group size had significant effects on brain size for Strepsirhini and Platyrrhini. I don't know if you could say that they had siginficantly different effects between groups unless you did a t test or something???? You could also maybe look at taxonomic group as an interaction with group size?? I tried to do this with the full model above. Maybe also a post-hoc test

```{r}
library(lmodel2)
library(broom)
tidy(m)
```
